Nail: A practical interface generator for data formats

### 2014-05-01 paper/osdi14/design.tex
pass through 3.3

\subsection{Dependent fields}
\label{s:dependent}
Data formats often contain values that are determined by other values or the layout of information,
such as checksums, duplicated information  or offset and  length fields.
We represent such as values with \emph{dependent fields} and handle them transparently during
parsing and generation without exposing them to the internal model.

Dependent fields are defined within a structure like normal fields, but their name starts with an $@$-sign. 
A dependent field is in scope and can be referred to by the definition of all subsequent fields in
the same structure. Dependency fields can be passed to rule invocations as parameters.

Dependent fields are parsed just like other fields in the external format, but they are not stored
in the internal data type. Instead, the parser stores the value in a
temporary location the field can be referenced by subsequent parsers.

When generating output, Nail visits a dependent field twice. First, while generating the other fields of a
structure, the generator reserves space for the dependent field in the output. Once
the dependent field goes out of scope, the generator  write the
dependent field's value to this space.

Nail only provides one built-in combinator, \cc{n_of} that uses dependency fields, which is used
for count fields. For example, DNS labels are encoded as Pascal-style strings: a length followed by
the value of the label. The Nail grammar for DNS labels can represent
this pattern as follows:

@@

Other dependencies, such as offset fields or checksums are not handled directly by combinators, but
through  transformations.

>>>>

\subsection{Dependent fields}
\label{s:dependent}
Data formats often contain values that are determined by other values or the layout of information,
such as checksums, duplicated information, or offset and  length fields.
We represent such values using \emph{dependent fields} and handle them transparently during
parsing and generation without exposing them to the internal model.

Dependent fields are defined within a structure like normal fields, but their name starts with an \cc{@} symbol.
A dependent field is in scope and can be referred to by the definition of all subsequent fields in
the same structure. Dependent fields can be passed to rule invocations as parameters.

Dependent fields are parsed just like other fields in the external format, but they are not stored
in the internal data type. Instead, the parser stores the value in a
temporary location, so that the field can be referenced by subsequent parsers.

When generating output, Nail visits a dependent field twice. First, while generating the other fields of a
structure, the generator reserves space for the dependent field in the output. Once
the dependent field goes out of scope, the generator  writes the
dependent field's value to this space.

Nail provides only one built-in combinator that uses dependent fields, \cc{n_of}, which is used
for count fields. For example, DNS labels are encoded as Pascal-style strings: a length followed by
the value of the label. The Nail grammar for DNS labels can represent
this pattern as:

@@

Other dependencies, such as offset fields or checksums, are not handled directly by combinators, but
through  transformations, as we describe next.
